### 2024-11-11 conteudo/background/linux.tex
add little preambulo to introduce chapter

>>>>

This chapter presents an overview of fundamental topics needed to understand 
the research, such as Linux Kernel, refactoring, types of code duplication, 
code duplication detection methods presented in the literature and ways to 
evaluating these methods. This foundation will make it easier to grasp the 
concepts discussed in the research.
